Continous time Markov chain models; \\ extension, simulation and visualisation

### 2015-02-09 chapters/chapter02.tex
implementing comments

Figure~\ref{fig:collapsing} illustrates this action for a branch that spans a single boundary at $T_1$ with $\mathbf{Q}_1$ governing the process before the boundary and $\mathbf{Q}_2$ after the boundary. Letting $X(T_1) = k$ represent the augmented state of the stochastic process at the boundary, we compute

@@

>>>>

Figure~\ref{fig:collapsing} illustrates this action for a branch that spans a single boundary at known time $T_1$ with $\mathbf{Q}_1$ governing the process before the boundary and $\mathbf{Q}_2$ after the boundary. Letting $X(T_1) = k$ represent the augmented state of the stochastic process at the boundary, we compute

@@

A tutorial which explains how to access the BEAST software comprising the `epoch model' accompanies this Chapter and can be found in Appendix~\ref{app:spread_tuto}.
